### 2013-05-03 paper/tex/design.tex
finish the paper

Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node, selected by the same hash function. We use a hash function to shard the queries because we consider the load balance of the Data Node which is much busier than Slave Node or Master Node in the system. In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job. Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the pressure at the Sink Node is significant which defects the whole system's throughput. Therefore, we have a solution accumulator attached to each Slave Node. The solution will be accumulated into a certain amount, then the Slave Node will report the results once.

\subsection{Framework Generalness}
An expected design goal of CloudCache is the generalness, we want to make this framework to be an proper and simply approach to solve many different types of hard problems in the cloud. According to the design, only two things need to be defined by the developer before using the framework. First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself. After finishing the two parts, the developer can submit a batch of problem as a job to the Master Node, where each problem is regarded as a task. Then the framework will start executing the batch job. In this section, we will show three hard problems' solution using CloudCache's framework.

>>>>

Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node, selected by the same hash function. We use a hash function to shard the queries because we consider the load balance of the Data Node which is much busier than Slave Node or Master Node in the system. In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job. Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the load at the Sink Node is significant which defects the whole system's throughput. Therefore, we have a small optimization that buffers the solution in each Slave Node until certain amount, then the Slave Node will report the buffered results together at once.

\subsection{Framework Generalness}
An expected design goal of CloudCache is the generalness, we want to make this framework to be a proper and simple approach to solve many different types of hard problems in the cloud. According to the design, only two things need to be defined by the developer before using the framework. First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself. After finishing the two parts, the developer can submit a batch of problem as a job to the Master Node, where each problem is regarded as a task. Then the framework will start executing the batch job. In this section, we will show two hard problems' solution using CloudCache framework.

### 2013-05-03 paper/tex/implementation.tex
framework performance
experiment done.
finish the paper

\subsection{Software Architecture}
We use Python as the language to implement the system. It consists of seven major modules in the source code.

@@

>>>>

\subsection{Software Architecture}
We use Python as the language to implement the system. It consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.

@@

\subsection{Implementation Optimizations}
After we implement the first version, we do not find too much advantages of the CloudCache framework. Thereafter, we analyze the code we write, and we realize the interaction between the Slave Node and Data Node are too frequent during the problem solving phase, which is reaching the benchmark upper bound of the Data Node. Each query and push operations costs more time than it should be. Therefore, we use a pipeline technique to solve the problem. Every time the problem is fully solved, either through cache query or brute-force, we put the result key-value pair into a pipeline. When the pipeline has certain number of solutions need to be cached in the cloud, we execute the whole pipeline once. This brings a decent performance gain for the CloudCache framework.

### 2013-05-03 paper/tex/performance.tex
finish the paper

\subsection{Problem Solving Performance}

@@

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_cpu.png}
  \caption{Master Node CPU}\label{fig:master_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_in.png}
  \caption{Master Node Network In}\label{fig:master_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_out.png}
  \caption{Master Node Network Out}\label{fig:master_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_cpu.png}
  \caption{Slave Node CPU}\label{fig:slave_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_in.png}
  \caption{Slave Node Network In}\label{fig:slave_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_out.png}
  \caption{Slave Node Network Out}\label{fig:slave_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_cpu.png}
  \caption{Sinker Node CPU}\label{fig:sinker_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_in.png}
  \caption{Sinker Node Network In}\label{fig:sinker_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_out.png}
  \caption{Sinker Node Network Out}\label{fig:sinker_out}
\endminipage\hfill
\end{figure*}

>>>>

\subsection{Problem Solving Performance}
One of the major performance metrics is the problem solving time, which shows how much time to solve a problem using CloudCache framework. In this evaluation, we generate $1,000,000$ problem instances randomly whose number of variables is between $1$ and $20$ and the number of clauses is between $1$ and $256$. We solve the $1,000,000$ twice: the first time we use brute-force approach by exhaustive search, and the second time we solve it within the CloudCache framework. During the experiments, we collect the time of each problem instance, then we draw a cumulative distribution frequency curve in Fig.~\ref{fig:time}.

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{pics/time.pdf}
\caption{The problem solving time CDF curve.}
\label{fig:time}
\end{figure}

As is shown in the figure, for easy problem instances, which usually can be  solved within a second, brute-force approach has more advantages. However, brute-force approach cannot benefit the hard problem instances at all, while the CloudCache framework can handle it very well. We think the linear scan and cache query process cost non-trivial amount of time for easy problem instances, but this time benefits the hard problem instances by reducing the exhaustive search into a simple validation process. Finally, it is safe to say the CloudCache framework is a good fit for the hard problem instances.

@@

\begin{figure*}
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_cpu.png}
  \caption{Master Node CPU}\label{fig:master_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_in.png}
  \caption{Master Node Network In}\label{fig:master_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_out.png}
  \caption{Master Node Network Out}\label{fig:master_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_cpu.png}
  \caption{Slave Node CPU}\label{fig:slave_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_in.png}
  \caption{Slave Node Network In}\label{fig:slave_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_out.png}
  \caption{Slave Node Network Out}\label{fig:slave_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_cpu.png}
  \caption{Sinker Node CPU}\label{fig:sinker_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_in.png}
  \caption{Sinker Node Network In}\label{fig:sinker_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_out.png}
  \caption{Sinker Node Network Out}\label{fig:sinker_out}
\endminipage\hfill
\end{figure*}
